Hydra Battles and Cie

### 2021-09-07 doc/part-hydras.tex
Fix compilation issues
minor changes

@@

\input{movies/snippets/Well_Orders/leastMemberDef}
\input{movies/snippets/Well_Orders/theLeast}

@@

The set  \texttt{AP} is  \emph{closed} under addition, and unbounded.

@@

@@

Lets us denote by $\varphi_\alpha$ the ordering function of the set $\textit{Cr}(\alpha)$ and by $A_\alpha$ its ordering segment.

>>>>

\subsection{A proof by computation}
\label{Ex42-E0}

It is interesting to compare the following proof of the equality
$\omega+42+\omega^2$ with the more theoretical proof in Sect~\vref{Ex42-schutte}.

\inputsnippets{E0/Ex42}

@@

\input{movies/snippets/Well_Orders/MDecl}
\input{movies/snippets/Well_Orders/theLeast}

@@

The set  \texttt{AP} is  \emph{closed} under addition, and unbounded.
\label{lemma:AP-plus-closed}

@@

\subsection{A last example}
\label{Ex42-schutte}

Let us prove again the equality $\omega+42+\omega^2= \omega^2$.Let us recall that $\omega^2$ is an abbreviation of $\phi_0(2)$,
\emph{i.e} the third  additive principal ordinal.

\inputsnippets{Schutte/Ex42a}

The proof is very different from the computational proof of Sect~\vref{Ex42-E0}.
By definition of additive principal ordinals, 
it suffices to prove the inequality $\omega+42< \phi_0(2)$ to get the equality we want to prove.

\inputsnippets{Schutte/Ex42b}

Since the set \texttt{AP} of additive principals  is closed under addition
(by Lemma \texttt{AP\_plus\_closed}, page~\pageref{lemma:AP-plus-closed}) , it suffices to prove the inequalities $\omega<\phi_0(2)$ and $42<\phi_0(2)$.

\input{movies/snippets/Schutte/Ex42d}

@@

Lets us denote by $\phi_\alpha$ the ordering function of the set $\textit{Cr}(\alpha)$ and by $A_\alpha$ its ordering segment.
